\documentclass{article}

\usepackage[printqrbox=false,printhint=false,printanswer=true,printmarkingguide=false,printclars=false]{unswalgos}

\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{shapes,fit}
\usepackage{tkz-fct}
\usepackage{wrapfig}
\usepackage{subfig}

\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{booktabs,multicol,multirow}
\usepackage{wasysym}
\usepackage{tcolorbox}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator{\NAND}{NAND}
\DeclareMathOperator{\AND}{AND}
\DeclareMathOperator{\OR}{OR}
\DeclareMathOperator{\NOT}{NOT}

\usepackage{xspace}

\fancyfoot[L]{\leftmark}
\fancyfoot[R]{\rightmark}

% This enables new paragraphs without indentation
\usepackage[parfill]{parskip}

\newcommand{\sem}{22T2}
\newcommand{\semester}{Term 2, 2022}
\SubjectNo{COMP3121/9101}
\newcommand{\taskname}{Assignment 2, Question 2}
\Institution{Jinghan Wang, z5286124} % Replace this with your name and zID


\begin{document}

\setcounter{question}{1}

\begin{Question}
There are $n$ towns in a line. A traveller starts at town $1$ and wants to reach town $n$. It takes a week to travel from any town to the next.

In each town, there is a market where you can buy rations. In the market of town $i$, you can buy a week's worth of rations for $c_i$ dollars. Furthermore, you can buy several weeks' rations for later consumption.

Your goal is to calculate the minimum cost to travel from town $1$ to town $n$.

\begin{Subquestion}
\textbf{[3 marks]} Which town's rations do you want to consume as you travel from town $n-1$ to town $n$? Provide reasoning to support your answer.

\begin{answer}
Answer:
\begin{quote}
    We hope to buy from the place with the lowest ration price before $n-1$.\\\\
    Suppose $P$ is the array of ration price, $i$ is the town's position, $n$ is the number of towns, $P[i]$ is the $ith$ town's ration price.
    \begin{itemize}
        \item [$\bullet$] If the minimum price during $[1, n - 1) < P[n-1]$, buy ration in the town with the minimum price.
        \item [$\bullet$] If the minimum price during $[1, n - 1) = P[n-1]$, buy ration in the town with the minimum price or in $(n-1)th$ town.
        \item [$\bullet$] If the minimum price during $[1, n - 1) > P[n-1]$, buy ration in $(n-1)th$ town.\\
    \end{itemize}
\end{quote}
\end{answer}
\end{Subquestion}

\begin{Subquestion}
\textbf{[3 marks]} When is the last time (if any) that you should change using from one town's rations to another? Provide reasoning to support your answer.

\begin{answer}
Answer:
\begin{quote}
    Suppose $P$ is the array of ration price, $i$ is the town's position, $P[i]$ is the $ith$ town's ration price, $n$ is the number of towns, the last time to buy is in $mth$ town.\\\\
    We hope thaSuppose $P$ is the array of ration price, $i$ is the town's position, $P[i]$ is the $ith$ town's ration price, the last time to buy is in $mth$ town.\\\\$P[i]_{min} = P[m]$ is the minimum price in array $P$.\\\\
    Because, when we find the least price during all towns, we can buy $n-m-1$ number of ration. $P[m]$ is the minimum price during all towns, therefore, $P[m] \times (n-m-1)$ is the minimum price which we paid after than $mth$ towns.\\

\end{quote}
\end{answer}
\end{Subquestion}

\clearpage
\begin{Subquestion}
\textbf{[14 marks]} Design an algorithm which runs in $O(n)$ time and achieves the goal.

\begin{answer}
Answer:
\begin{quote}
    Suppose $P$ is the array of ration price, $N$ is the number of ration purchased, $i$ is the town's position,$m$ record the minimum position during the array $P$, $n$ is the number of towns\\\\
    First, we must buy ration in the first town because we do not carry any ration during the traveling, set $m = 1$ and $N[1] = 1$.\\\\
    Because when we reach $nth$ town, the traveling is finished, therefore, we do not need to buy in the last town.\\ 
    Now, perform the following step while $ i > 1 \AND i < n $:
    \begin{itemize}
        \item [$\bullet$] if $P[i] >= P[m]$, $N[m] = N[m] + 1$ and continue.
        \item [$\bullet$] if $P[i] < P[m]$, $N[i] = 1$ and $m = i$ than continue.\\
    \end{itemize}
    The time complexity is $O(n)$\\\\
    After that, traverse the array $N$ again, the time complexity is $O(n)$ and we can get the number of ration which need to buy in each towns, the minimum total price is the sum value of array $N$.\\\\
    Therefore, the total time complexity is $O(n)$.\\
\end{quote}
\end{answer}
\end{Subquestion}
\end{Question}

\end{document}